disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-21 article.Rnw
Gotta keeo line length below 80 I tihnk.

# Make a RasterStack of covariates to the extent of Madagascar and scale values
covariates <- lapply(covariate_raster_paths, raster)
covariate_stack <- stack(covariates)
covariate_stack <- scale(crop(covariate_stack, extent(c(42, 52, -26, -10))))

>>>>

# Make a RasterStack of covariates, 
# crop to the extent of Madagascar and scale values
covariates <- lapply(covariate_raster_paths, raster)
covariate_stack <- stack(covariates)
covariate_stack <- scale(crop(covariate_stack, extent(c(42, 52, -26, -10))))
